Carbonate chemistry at Ny-Ålesund

### 2021-03-08 awipev-CO2.Rmd
delete big figs objects; add chunk boxplots

# Combine plots
g <- (ts_sal / ts_temp / ts_par_air / ts_pCO2 / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
#rm(ls(pattern = "ts_"))

#save_plot(filename = "figures/time_series.png", plot = g)
#g_cw <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
```
## Maintenance
<div style="text-align: justify">

>>>>

# Combine plots
g <- (ts_sal / ts_temp / ts_par_air / ts_pCO2 / ts_pH / ts_at)
g <- g + plot_annotation(tag_levels = 'A')
ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
rm(list = ls(pattern = "ts_")) #delete big ggplot objects
gc() #garbage collection
#save_plot(filename = "figures/time_series.png", plot = g)
#g_cw <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
```
## Maintenance
<div style="text-align: justify">
